---
title: "Activity 11 - Practicing with Intervals for Differences"
author: "STS 2300 (Dr. VanKrevelen)"
date: 'Updated: 4/9/2024'
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Below are the packages you will need for this activity. If you use other packages, you can add them here.

```{r, message = FALSE}
library(ggplot2)
library(infer)
library(dplyr)
```

---


# Part 1 - Fidget spinners and attention

A study looked at the effect that fidget spinners have on attention and memory. You can read an article about it [here](https://www.psypost.org/2019/11/study-finds-using-a-fidget-spinner-can-impair-memory-and-attention-54904) or look at the research paper [here](https://onlinelibrary.wiley.com/doi/full/10.1002/acp.3610) if you're interested.

The researchers wanted to know how attention might differ between people using and not using a fidget spinner. The code below will read data from the study directly into R and subset the data to remove a control group where no fidget spinner was used. This leaves us with two groups in the `Condition` variable: "Spinner" (actively using a fidget spinner) and "Spinner Present" (near someone who was using a fidget spinner).

```{r}
fidget <- read.csv("https://raw.githubusercontent.com/vank-stats/STS2300-Spring2024/main/data/fidget_spinners.csv") %>%
  filter(Condition != "No Spinner")
```

<br>


1. Create a graph that can be used to explore how `AttentionScore` differs between people using a fidget spinner and people near someone using a fidget spinner. Describe what the graph shows about the distribution of `AttentionScore` between these two groups.

```{r}

```

**Graph description:**

<br>


2. Calculate a difference in sample mean attention scores between the two groups. Use "Spinner" - "Spinner Present" as the order of subtraction. Write a sentence about what the value you get means in context of this example. Additionally, write out a sentence describing the corresponding paramater of interest.

```{r}

```

**Sentence about difference in sample means:**

**Parameter of interest:**

<br>


3. Generate a bootstrap distribution to better understand sampling variability in your estimate. Make a histogram of this distribution and comment on what you see. (Note: The `set.seed()` line will ensure we get the same result each time we knit our document. You should replace the number with a number of your choosing.)

```{r}
set.seed(92520)

```

**Description of bootstrap:**

<br>


4. Calculate a confidence interval for the difference in population means that uses your bootstrap distribution. Write your interval below. (Note: I didn't specify a confidence level, so you can choose one)

```{r}

```

**CI:**

<br>


5. Provide an interpretation of your confidence interval in context of this example. Additionally, consider whether it seem like fidget spinners help (or hurt) memory on average?

**Interpretation:**

<br>


6. Based on your results, what takeaways can we make (or not make) about the impact of fidget spinners on attention?

**Answer:**

<br>


7. For practice, make a theory-based confidence interval for this example as well.

```{r}

```

**CI:**

<br>


8. How broadly do you think these conclusions (from your CI) might apply? Consider who makes up the sample and whether you think it's likely this was a random sample.

**Answer:**

<br>


---


# Part 2 - COVID-19 Identifying Dog (Revisited)

In Activity 10, we analyzed some data from a dog who was trained to detect COVID-19 by smell. However, we only considered the times when the dog was presented with a sample that contained COVID-19. The actual experiment included cases with and without COVID-19. Below is code to read in the full data.

```{r}
covid_dog <- data.frame(ID = c(rep("positive", 157), rep("negative", 792),
                               rep("positive", 33), rep("negative", 30)),
                        actual = c(rep("positive", 157), rep("negative", 792),
                                   rep("negative", 33), rep("positive", 30))) %>%
  mutate(correct = factor(ID == actual))
```

<br>


9. Make a bar graph (using `geom_bar()`) to compare the proportion of cases that the dog correctly identifies among those with and without COVID-19. To do this, you will map `actual` (our two groups) to the x axis and `correct` to the fill argument. Use `position = "fill"` inside `geom_bar()` to display proportions instead of counts. What does the graph show about how well the dog does in each type of sample?

```{r}

```

**Answer:**

<br>


10. What is the parameter of interest for this example? Write it out in words below.

**Parameter of interest:**

<br>


11. We can calculate point estimates by writing code for a bootstrap distribution but leaving out the `generate()` argument (i.e. only using `specify()` and `calculate()`). Calculate a difference in sample proportions in this way and explain what the value you get means in this context.

```{r}

```

**Answer:**

<br>


12. Write code to generate a bootstrap distribution. You can reuse your code from the previous question and add in a `generate()` line between `specify()` and `calculate()`. Describe what your bootstrap distribution shows. (Note: Remember to set a seed)

```{r}

```

**Description:**

<br>


13. Generate a 95% confidence interval using your bootstrap distribution.

```{r}

```

**95% CI:**

<br>


14. Interpret your interval in context of this example. Your sentence should be understandable by someone reading a news story abou this dog. (Note: When talking about a difference in percentages, you will use the phrase "percentage points")

**Interpretation:**

<br>


15. The article mentioned the dog might be able to be used at airports or other locations to determine if someone has COVID-19. What might we need to consider about the applicability of these results outside the context of the experiment? (Note: It might help to read how the dog was tested or to watch the short video)

**Answer:**

<br>


16. As practice, calculate a 95% theory-based interval based on this data.

```{r}

```

**95% CI:**
