---
title: "Activity 11 - Practicing with Intervals for Differences (Solutions)"
author: "STS 2300 (Dr. VanKrevelen)"
date: 'Updated: 4/9/2024'
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Below are the packages you will need for this activity. If you use other packages, you can add them here.

```{r, message = FALSE}
library(ggplot2)
library(infer)
library(dplyr)
```

---


# Part 1 - Fidget spinners and attention

A study looked at the effect that fidget spinners have on attention and memory. You can read an article about it [here](https://www.psypost.org/2019/11/study-finds-using-a-fidget-spinner-can-impair-memory-and-attention-54904) or look at the research paper [here](https://onlinelibrary.wiley.com/doi/full/10.1002/acp.3610) if you're interested.

The researchers wanted to know how attention might differ between people using and not using a fidget spinner. The code below will read data from the study directly into R and subset the data to remove a control group where no fidget spinner was used. This leaves us with two groups in the `Condition` variable: "Spinner" (actively using a fidget spinner) and "Spinner Present" (near someone who was using a fidget spinner).

```{r}
fidget <- read.csv("https://raw.githubusercontent.com/vank-stats/STS2300-Spring2024/main/data/fidget_spinners.csv") %>%
  filter(Condition != "No Spinner")
```

<br>


1. Create a graph that can be used to explore how `AttentionScore` differs between people using a fidget spinner and people near someone using a fidget spinner. Describe what the graph shows about the distribution of `AttentionScore` between these two groups.

```{r}
# One possibility
ggplot(fidget, aes(x = AttentionScore)) +
  geom_histogram(color = "white", binwidth = 0.5) +
  facet_wrap(vars(Condition), ncol = 1)

# Another possibility
ggplot(fidget, aes(x = AttentionScore, y = Condition)) +
  geom_boxplot()
```

**Graph description:** We can see that attention score tends to be higher for the Spinner group than for Spinner Present group (e.g. higher Q1, median, and Q3). There isn't a huge difference between the two groups though.

<br>


2. Calculate a difference in sample mean attention scores between the two groups. Use "Spinner" - "Spinner Present" as the order of subtraction. Write a sentence about what the value you get means in context of this example. Additionally, write out a sentence describing the corresponding parameter of interest.

```{r}
fidget_xbardiff <- fidget %>%
  specify(AttentionScore ~ Condition) %>%
  calculate(stat = "diff in means", order = c("Spinner", "Spinner Present"))
fidget_xbardiff
```

**Sentence about difference in sample means:** The sample mean attention score is 0.404 points higher for those using a spinner than for those near someone using one.

**Parameter of interest:** The population mean difference in attention score for those using a spinner minus those near someone using a spinner.


<br>


3. Generate a bootstrap distribution to better understand sampling variability in your estimate. Make a histogram of this distribution and comment on what you see. (Note: The `set.seed()` line will ensure we get the same result each time we knit our document. You should replace the number with a number of your choosing.)

```{r}
set.seed(92520)
fidget_boot <- fidget %>%
  specify(AttentionScore ~ Condition) %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in means", order = c("Spinner", "Spinner Present"))
visualize(fidget_boot)
```

**Description of bootstrap:** The bootstrap distribution is bell-shaped and centered on our difference in sample means of 0.404. It contains values from just under 0 to just over 0.8.

<br>


4. Calculate a confidence interval for the difference in population means that uses your bootstrap distribution. Write your interval below. (Note: I didn't specify a confidence level, so you can choose one)

```{r}
fidget_boot %>%
  get_ci(type = "percentile", level = 0.99)
```

**99% CI (percentile method):** (-0.066, 0.929)

<br>


5. Provide an interpretation of your confidence interval in context of this example. Additionally, consider whether it seem like fidget spinners help (or hurt) memory on average?

**Interpretation:** We cannot be 99% confident that the population mean attention score differs for those using fidget spinners and those near someone using one. However, we are 99% confident that the population mean attention score is anywhere from 0.066 higher for people near someone using a fidget spinner to 0.929 higher for people that are using the fidget spinner themselves.

<br>


6. Based on your results, what takeaways can we make (or not make) about the impact of fidget spinners on attention?

**Answer:** Based on our 99% confidence interval, we cannot be confident that fidget spinners are impacting average attention score between these two groups. (Note: However, if we had made a 90% confidence interval, we would have been 90% confident the people using the fidget spinner had a higher population mean.)

<br>


7. For practice, make a theory-based confidence interval for this example as well.

```{r}
t.test(AttentionScore ~ Condition, data = fidget, conf.level = 0.99)
```

**CI:** (-0.111, 0.919)

<br>


8. How broadly do you think these conclusions (from your CI) might apply? Consider who makes up the sample and whether you think it's likely this was a random sample.

**Answer:** Everyone in the sample is between 18 and 23, so I probably would want to restrict my conclusions to people in this age range. This almost certainly was not a random sample from a population of 18 to 23 year olds. Probably people volunteered to be in the study.

<br>


---


# Part 2 - Airbnb Discrimination

The code below will read a data frame into R from a study on potential discrimination by Airbnb hosts. In the experiment, researchers sent requests to Airbnb hosts asking to stay at their properties. The only difference on each request was the name that was used. Researchers chose names that were predominantly associated with certain genders and races (determined in a separate study) and randomly assigned a name to each request. They then recorded whether or not the host gave a positive response indicating the person could stay there. 

Our goal will be to determine the difference in proportion of positive responses given by hosts who received a request from a predominantly Black name versus a predominantly white name.

```{r}
airbnb <- read.csv("https://raw.githubusercontent.com/vank-stats/STS2300-Spring2024/main/data/airbnb.csv")
```

<br>


9. Make a bar graph (using `geom_bar()`) to compare the proportion of positive responses between the two races used in this study. Briefly describe what the graph shows about our sample. (Note: You want your variable that creates groups (`Race`) to go on the x-axis and your variable of interest (`Response`) to map to fill. Use the `position = "fill"` argument inside `geom_bar()` to get a graph comparing proportions.)

```{r}
ggplot(airbnb, aes(x = Race, fill = Response)) +
  geom_bar(position = "fill")
```

**Description of graph:** The proportion of positive responses in the sample is higher when the host perceives the requestor's race to be White than when they perceive it to be Black. Eyeballing this it looks like the proportion for the White group is about 0.08 higher.

<br>


10. What is the parameter of interest for this example? Write it out in words below.

**Parameter of interest:** The difference in population proportion of positive responses when the request is from a predominantly Black name versus a predominantly White name.

<br>


11. We can calculate point estimates by writing code for a bootstrap distribution but leaving out the `generate()` argument (i.e. only using `specify()` and `calculate()`). Calculate a difference in sample proportions in this way and explain what the value you get means in this context.

```{r}
airbnb_diffinxbars <- airbnb %>%
  specify(Response ~ Race, success = "Positive") %>%
  calculate(stat = "diff in props", order = c("Black", "White"))
airbnb_diffinxbars
```

**Answer:** In our sample, the proportion of positive responses was around 0.085 lower for predominantly Black names than for predominantly White names.

<br>


12. Write code to generate a bootstrap distribution. You can reuse your code from the previous question and add in a `generate()` line between `specify()` and `calculate()`. Describe what your bootstrap distribution shows. (Note: Remember to set a seed)

```{r}
set.seed(5328412)
airbnb_boot <- airbnb %>%
  specify(Response ~ Race, success = "Positive") %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "diff in props", order = c("Black", "White"))
visualize(airbnb_boot)
```

**Description:** The bootstrap distribution is roughly bell-shaped and centered around our difference in sample proportions of -0.085. It contains values from below -0.12 up to almost -0.04.

<br>


13. Generate a 95% confidence interval using your bootstrap distribution.

```{r}
airbnb_boot %>%
  get_ci(level = 0.95, type = "se", point_estimate = airbnb_diffinxbars)
```

**95% CI:** (-0.109, -0.061)

<br>


14. Interpret your interval in context of this example. Your sentence should be understandable by someone reading a news story about this experiment. (Note: When talking about a difference in percentages, you will use the phrase "percentage points")

**Interpretation:** We are 95% confident that the population proportion of positive responses from Airbnb hosts is between 0.061 and 0.109 lower when the request is from a predominantly Black name than when it is from a predominantly White name.

<br>


15. As practice, calculate a 95% theory-based interval based on this data.

```{r}
table(airbnb$Response, airbnb$Race)
prop.test(x = c(1210, 1498),
          n = c(1210 + 1900, 1498 + 1661),
          conf.level = 0.95)
```

**95% CI:** (-0.110, -0.060)
