---
title: "Unit 3 Supplement"
output: html_document
date: "2024-04-15"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Confidence interval conditions / assumptions

All confidence interval methods that we will cover only work when the data comes from a random sample of the population.

The methods will then have other conditions that need to me met for them to work. These conditions will vary from parameter to parameter or between theory-based and bootstrap methods.


## Theory-based method conditions

### CI for p

1. The data is a random sample from the population
2. The sample size is "big enough" (one possible way to assess this is to check that you have at least 5 successes and 5 failures in your data)
3. The sample isn't too much of the population (one possible approach is to say the sample is less than 1/20th of the population)

Note: There is something called a finite population correction that can be used if condition 3 is not met


### CI for p1 - p2

1. The data is a random sample from the population
2. Both sample sizes are "big enough" (one possible way to assess this is to check that you have at least 5 successes and 5 failures in your data)
3. Neither sample isn't too much of the population (unless you use finite population correction)


### CI for mu

1. The data is a random sample from the population
2. The population is approximately normal (or our sample is "big enough")

Note: In most cases "big enough" means n > 30 for examples for $\mu$ or $\mu_1 - \mu_2$.


### CI for mu1 - mu2

1. The data is a random sample from the population
2. Both populations are approximately normal (or both samples are "big enough")
3. (Sometimes) The population variances are equal (There are multiple versions of this test. Some require condition 3 and some do not. The default in `t.test()` is a method that does not require this condition)


## Bootstrap interval conditions

### SE Method

1. The data is a random sample from the population
2. The *bootstrap distribution* is approximately normal


### Percentile Method

1. The data is a random sample from the population

Note: This method works when the other methods work and potentially in additional cases unless some pretty weird things are going.


---


# Example of when theory-based and SE methods wouldn't work

**Background**: Someone has recorded whether or not it rained for each of 45 days. It rained on only one day and they want to make a confidence interval for the population proportion of days that it will rain there.

Theory-based CI: We do not have at least 5 successes, so this method is not recommended.

SE Method: The bootstrap distribution is skewed right and not bell-shaped, so this method is not recommended.

Percentile method should still work

```{r, message = FALSE}
library(infer)
library(dplyr)

rain <- data.frame(rained = c("yes", rep("no", 44)))

set.seed(958)
rain_boot <- rain %>%
  specify(rained ~ NULL, success = "yes") %>%
  generate(reps = 1000, type = "bootstrap") %>%
  calculate(stat = "prop")
visualize(rain_boot)

rain_boot %>%
  get_ci(type = "percentile")

rain_boot %>%
  get_ci(type = "se", point_estimate = 1/45)

prop.test(x = 1, n = 45)$conf.int %>% round(4)
```

Notice how the SE method contains negative values and the theory-based method contains values MUCH larger than the other two methods.

